Structure Learning for Causal Decision Making

### 2019-03-03 UAI_2019/UAI_Draft.tex
cambios en related work

\section{Related Work}

In \cite{lattimoreNIPS2016}, the problem of finding a best intervention over a known causal model for a fixed number of learning trials is considered and it was found that by considering causal information a \textit{faster} optimal-action learning can be achieved. Their assumption of knowing the causal model was relaxed by \cite{sen2017identifying} who considers a partially known causal model and allows interventions over a the unknown part of the model. In \cite{gonzalez2018playing} it was proposed that a rational decision maker can find an optimal action by holding \textit{beliefs} about the existence and strength of causal relations and by using those beliefs \textit{as if} they were the true relations in order to make a choice and then updating those beliefs after observing what the chosen action \textit{caused} good actions can be found. Such procedure implicitly considers a distribution over Causal Graphical Models, where each structure is used within each step in otder to make a choice by considering his causal knowledge as it if were true, as proposed by \cite{joyce1999foundations}. Their work assumes that the decision maker knows the structure, but not the associated parameters, of the model. Later, \cite{2019arXiv190202279G}, such authors formalize that procedure by stating a formal criteria which has the form:
\[  a^\ast = \textrm{ argmax }_{a \in \mathcal{A}}\sum_g P(Y=1 | do(a), g)P(g), \]
where $\mathcal{A}$ is the set of available actions to the decision maker and $1$ is the most desired value of the \textit{objective variable} $Y$, for the decision maker. We notice that since the action chosen is the action with the highest probability of causally producing the most desired action, then $a^\ast$ necesarilly is the action that maximizes the expected utility for the agent. The function above described is indeed a counterfactual distribution, since it allows to compare the probability of causing a desired actions by alternative actions that were not chosen.

>>>>

\section{Related Work}
In \cite{lattimoreNIPS2016}, the problem of finding a best intervention over a known causal model for a fixed number of learning trials is considered and it was found that by considering causal information a \textit{faster} optimal-action learning can be achieved. Their assumption of knowing the causal model was relaxed by \cite{sen2017identifying} who considers a partially known causal model and allows interventions over a the unknown part of the model.

In \cite{gonzalez2018playing} it was proposed that a rational decision maker can find an optimal action by holding \textit{beliefs} about the existence and strength of causal relations and by using those beliefs \textit{as if} they were the true relations in order to make a choice and then updating those beliefs after observing what the chosen action \textit{caused} good actions can be found. Such procedure implicitly considers a distribution over Causal Graphical Models, where each structure is used within each step in otder to make a choice by considering his causal knowledge as it if were true, as proposed by \cite{joyce1999foundations}. Their work assumes that the decision maker knows the structure, but not the associated parameters, of the model.

Later, \cite{2019arXiv190202279G}, such authors formalize that procedure by stating a formal criteria which has the form:
\[  a^\ast = \textrm{ argmax }_{a \in \mathcal{A}}\sum_g P(Y=1 | do(a), g)P(g), \]
where $\mathcal{A}$ is the set of available actions to the decision maker and $1$ is the most desired value of the \textit{objective variable} $Y$, for the decision maker. We notice that since the action chosen is the action with the highest probability of causally producing the most desired action, then $a^\ast$ necesarilly is the action that maximizes the expected utility for the agent. The function above described is indeed a counterfactual distribution, since it allows to compare the probability of causing a desired actions by alternative actions that were not chosen.
